### 2015-05-12 whoop.tex
update in main section

Symbolic pairwise lockset analysis works by considering, for a given driver, every pair of entry points that can potentially execute concurrently.  For each such pair, we use symbolic verification to check whether it is possible for the pair to race, modeling the effects of additional entry points by treating the driver shared state abstractly: when an entry point reads from the shared state, a nondeterministic value is returned.  Symbolic verification of an entry point pair works by (i) instrumenting each entry point with additional state to record locksets (see Section~\ref{bg:lockset}), and (ii) attempting to verify a sequential program that executes the instrumented entry points in sequence and then asserts that the lockset for each shared variable is non-empty.  Verification of the resulting sequential program can be undertaken using any sound method; in practice we employ the Boogie verification engine~\cite{barnett2006boogie}, which requires procedure specifications and loop invariants to be generated, after which verification conditions are generated and discharged to an automated theorem prover.

>>>>

Our approach considers, for a given driver, every pair of entry points that can potentially execute concurrently.  For each such pair, we use symbolic verification to check whether it is possible for the pair to race in a shared variable. We soundly model the effects of additional entry points by treating the driver shared state abstractly: when an entry point reads from the shared state, a nondeterministic value is returned.

Symbolic verification of a pair of entry points works by (i) instrumenting each entry point with additional state to record locksets, and (ii) attempting to verify a sequential program that executes the instrumented entry points in sequence and then asserts that the lockset for each shared variable is non-empty.  Verification of the resulting sequential program can be undertaken using any sound method; in practice we employ the Boogie verification engine~\cite{barnett2006boogie}, which requires procedure specifications and loop invariants to be generated, after which verification conditions are generated and discharged to an automated theorem prover.
